\setlength{\parskip}{0pt}
\section{Postdoctoral Research Experience}
Postdoctoral Research Associate \hfill February 2015 - Present\\
CMS Experiment, Fermi National Accelerator Laboratory, Batavia, IL 60510 USA\\
Supervisors: {\sl Frank Chlebana} (\href{mailto:chlebana@fnal.gov}{chlebana@fnal.gov}), {\sl Daniel Elvira} (\href{mailto:daniel@fnal.gov}{daniel@fnal.gov})\\
Leadership:
\begin{itemize}[leftmargin=12pt]
\item Maintainer and primary developer for \href{https://github.com/TreeMaker/TreeMaker}{TreeMaker} ntuple production software, used for numerous searches.
\item L3 HCAL CMSSW Co-convener (2016-2017); leading developer for HCAL Phase 1 software.
\item L3 Upgrade Simulation and Reconstruction Coordinator (2016)
\item L2 Upgrade Software Coordinator (2017-present)
\item Deputy Release Manager for CMSSW (2018-present)
\end{itemize}
Projects:
\begin{itemize}[leftmargin=12pt]
\item Searching for supersymmetry in the multijets plus missing energy final state.
\item Searching for evidence of strongly-coupled dark matter from hidden sectors in the form of semi-visible jets.
\item Testing new striped data analysis framework, which uses NoSQL and Python tools to process up to 20M events/sec.
\item Developing SONIC (Services for Optimized Network Inference on Coprocessors) for CMSSW with jet images.
\item Integrating and testing the GeantV vectorized transport engine in the CMS software framework.
\item Developing reconstruction algorithms and software for the High Granularity Calorimeter.
\item Supervised and consulted on HCAL radiation damage studies in simulation and collision data.
\end{itemize}
