\section{Undergraduate Research Experience}
\begin{itemize}[leftmargin=12pt]
\item Daya Bay Experiment - Undergraduate Research Assistant \hfill January 2008 - August 2011\\
Rensselaer Polytechnic Institute, Troy, NY 12180 USA\\
Supervisors: {\sl Jim Napolitano} (\href{mailto:napolj@temple.edu}{napolj@temple.edu}), {\sl John Cummings} (\href{mailto:jcummings@siena.edu}{jcummings@siena.edu})
\begin{itemize}
% \item Created and maintained hardware and software solutions for data acquisition, analysis, and communication among the RPI collaboration.
\item Created and maintained hardware and software solutions for data acquisition, analysis, and communication at RPI.
\item Used a WetLabs C-Star transmissometer to study attenuation lengths in ultra-pure water.
\item Worked to understand the slow controls system and database that will be installed in China.
\end{itemize}
\item ATLAS Experiment - Undergraduate Research Assistant \hfill January 2011 - May 2011\\
The University at Albany, Albany, NY 12222 USA\\
Supervisor: {\sl Jesse Ernst} (\href{mailto:jae@albany.edu}{jae@albany.edu})
\begin{itemize}
\item Documented, debugged, improved, and added to the TriggerFish software, which is designed to make fast estimates of trigger rates for the ATLAS experiment.
\end{itemize}
\item CMS Experiment - REU Student \hfill June 2010 - August 2010\\
Fermi National Accelerator Laboratory, Batavia, IL 60510 USA\\
Supervisors: {\sl Aran Garcia-Bellido} (\href{mailto:aran@pas.rochester.edu}{aran@pas.rochester.edu}), {\sl Marek Zielinski} (\href{mailto:marek@fnal.gov}{marek@fnal.gov})
$\newline$ Worked with the CMS JetMET group through the University of Rochester REU, on the following:
\begin{itemize}
\item Optimized a procedure to extrapolate absolute jet response from photon + jet events.
\item Investigated relative jet responses and resolutions for different types of reconstructed jets (included in CMS PAS JME-10-003).
\item Studied heavy and light flavor quark contributions to jet responses and missing jet energy.
\end{itemize}
\item CMS Experiment, CLIC Test Facility 3 - CERN Summer Student \hfill June 2009 - August 2009\\
European Organization for Nuclear Research (CERN), Geneva, Switzerland\\
Supervisors: {\sl Mayda Velasco} (\href{mailto:mayda.velasco@cern.ch}{mayda.velasco@cern.ch}), {\sl Anne Dabrowski} (\href{mailto:anne.dabrowski@cern.ch}{anne.dabrowski@cern.ch})
\begin{itemize}
\item Analyzed Monte Carlo simulations of backgrounds for t-tbar events in order to search for flavor-changing neutral currents at the LHC. (CMS)
\item Performed error analysis on measurements of electron bunch length and shape. (CTF3)
\end{itemize}
\end{itemize}