\section{Teaching\\Experience}
\begin{itemize}[leftmargin=12pt]
\item Fundamentals of Physics II - Graduate Teaching Assistant \hfill January 2012 - May 2012\\
University of Maryland, College Park, MD 20742 USA\\
Supervisor: {\sl Eun-Suk Seo} (\href{mailto:seo@umd.edu}{seo@umd.edu})
\begin{itemize}
\item Led tutorials and labs and held office hours in the course center.
\item Graded homework, lab reports, and exams.
\end{itemize}
\item General Physics: Mechanics and Particle Dynamics - Graduate Teaching Assistant \hfill August 2011 - December 2011\\
University of Maryland, College Park, MD 20742 USA\\
Supervisors: {\sl Darayash Tata} (\href{mailto:dtata@umd.edu}{dtata@umd.edu}), {\sl James Lavine} (\href{mailto:jplavine@umd.edu}{jplavine@umd.edu})
\begin{itemize}
\item Led discussion sections and held office hours.
\item Graded quizzes and exams.
\end{itemize}
\item Honors Physics I \& II - Undergraduate Teaching Assistant \hfill August 2008 - May 2011\\
Rensselaer Polytechnic Institute, Troy, NY 12180 USA\\
Supervisors: {\sl Jim Napolitano} (\href{mailto:napolj@temple.edu}{napolj@temple.edu}), {\sl Peter Persans} (\href{mailto:persap@rpi.edu}{persap@rpi.edu}), {\sl Gyorgy Korniss} (\href{mailto:korniss@rpi.edu}{korniss@rpi.edu})
\begin{itemize}
\item Assisted students with lab equipment, data analysis, and homework problems.
\item Assisted the graduate teaching assistants in grading homework, lab reports, and tests.
\end{itemize}
\item Using Matlab, Maple, and Mathematica for Physics - Teaching Assistant \hfill August 2010 - December 2010\\
Rensselaer Polytechnic Institute, Troy, NY 12180 USA\\
Supervisor: {\sl Jim Napolitano} (\href{mailto:napolj@temple.edu}{napolj@temple.edu})
\begin{itemize}
\item Contributed to curriculum development and lesson planning.
\item Assisted students with in-class exercises.
\item Graded in-class exercises.
\end{itemize}
\end{itemize}